From clusters to queries: exploiting uncertainty in the modularity landscape of complex networks

### 2018-05-01 article/article.tex
gos

\begin{figure}[ht]
    \includegraphics[width=0.45\textwidth]{images/search_space_3.png}
    \caption{Modularity search space of an \textit{E. coli} metabolic network.
 Distance between partitions is calculated using variation of information \cite{meilua2003comparing} and dimensionality reduction is performed using curvilinear component analysis \cite{demartines1997curvilinear}.
  The inset (top) demonstrates the landscape of the high modularity region. 
  Figure generated with the software of Good \textit{et al.}\cite{good2010performance}.}
    \label{fig:modular_search_space}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.45\textwidth]{images/meth_fig/fig1_desc.eps}
    \caption{Outline of the proposed approach to querying networks by using multiple, high quality representations of modular networks.}
    \label{fig:algorithm_outline}
\end{figure}

@@

\begin{figure*}[ht]
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/lfr_binary_mo_overlap_auc_1000.eps}
        \caption{1000 nodes}
    \end{subfigure}
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/lfr_binary_mo_overlap_auc_5000.eps}
        \caption{5000 nodes}
    \end{subfigure}
    \caption{Non-overlapping community varying seed nodes on LFR networks with 1000 and 5000 nodes.
     Data points represent mean auc scores for all communities on 100 sampled networks at varying mixing coefficients.
     Error bars represent standard deviations.}
     \label{fig:auc_no_overlap}
\end{figure*}

@@

\begin{figure*}[ht]
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/lfr_binary_overlap_auc_1000.eps}
        \caption{1000 nodes}
    \end{subfigure}
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/lfr_binary_overlap_auc_5000.eps}
        \caption{5000 nodes}
    \end{subfigure}
    \caption{Overlapping community varying seed nodes on LFR networks with 1000 and 5000 nodes.
     Data points represent mean auc scores for all communities on 100 sampled networks at varying overlapping fraction of nodes.
     Error bars represent standard deviations.}
     \label{fig:auc_overlap}
\end{figure*}

@@

\begin{figure*}[ht]
\includegraphics[width=\textwidth]{images/ppi_example_combined.eps}
\caption{An example of the GO term \textit{``SNAP receptor activity''} (16 nodes) on the \textit{Arabidopsis thaliana} protein-protein interaction network.
(A) Shows the full network with 3 randomly chosen query nodes from the full query set.
(B) Shows a reduced view of the network where a threshold of $\mu_i(S) > 0.8$ is selected, reducing the network to 404 nodes.
Blue nodes indicate those in the randomly selected 3 query nodes, yellow the remaining nodes in the term and the shade of red relates to the strength of the relationship each node has to the query set.
(C) Shows an example ROC curve from the cross validation described in the main text. 
Based on 3 randomly selected query nodes containing this GO term.
}
\label{fig:query_example}
\end{figure*}

@@

 \item \textbf{Yeast protein-protein interaction network (Yeast PPI)} \cite{yeast_ppi}
 This dataset is a collection of recorded binary interactions between proteins collected with high-throughput yeast-2-hybrid assays.
 The metadata used are known, experimentally validated protein complexes from \cite{yeast_ppi_complexes}.
 The network contains 6222 nodes in the largest connected component, with 22,3868 edges.
 There are 409 experimentally validated protein complexes, 236 of which contain 3 or more nodes.
 The protein complexes are typically very small in terms of number of proteins with  90\% of the complexes containing less than 10 proteins and only 2 complexes containing 50 or more proteins.

>>>>

\begin{figure}[t]
    \includegraphics[width=0.45\textwidth]{images/search_space_3.png}
    \caption{Modularity search space of an \textit{E. coli} metabolic network.
 Distance between partitions is calculated using variation of information \cite{meilua2003comparing} and dimensionality reduction is performed using curvilinear component analysis \cite{demartines1997curvilinear}.
  The inset (top) demonstrates the landscape of the high modularity region. 
  Figure generated with the software of Good \textit{et al.}\cite{good2010performance}.}
    \label{fig:modular_search_space}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.45\textwidth]{images/meth_fig/fig1_desc.eps}
    \caption{Outline of the proposed approach to querying networks by using multiple, high quality representations of modular networks.}
    \label{fig:algorithm_outline}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/lfr_binary_mo_overlap_auc_1000.eps}
        \caption{1000 nodes}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/lfr_binary_mo_overlap_auc_5000.eps}
        \caption{5000 nodes}
    \end{subfigure}
    \caption{Non-overlapping community varying seed nodes on LFR networks with 1000 and 5000 nodes.
     Data points represent mean auc scores for all communities on 100 sampled networks at varying mixing coefficients.
     Error bars represent standard deviations.}
     \label{fig:auc_no_overlap}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/lfr_binary_overlap_auc_1000.eps}
        \caption{1000 nodes}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/lfr_binary_overlap_auc_5000.eps}
        \caption{5000 nodes}
    \end{subfigure}
    \caption{Overlapping community varying seed nodes on LFR networks with 1000 and 5000 nodes.
     Data points represent mean auc scores for all communities on 100 sampled networks at varying overlapping fraction of nodes.
     Error bars represent standard deviations.}
     \label{fig:auc_overlap}
\end{figure}

@@

\begin{figure*}[t]
\includegraphics[width=\textwidth]{images/ppi_example_combined.eps}
\caption{An example of the GO term \textit{``SNAP receptor activity''} (16 nodes) on the \textit{Arabidopsis thaliana} protein-protein interaction network.
(A) Shows the full network with 3 randomly chosen query nodes from the full query set.
(B) Shows a reduced view of the network where a threshold of $\mu_i(S) > 0.8$ is selected, reducing the network to 404 nodes.
Blue nodes indicate those in the randomly selected 3 query nodes, yellow the remaining nodes in the term and the shade of red relates to the strength of the relationship each node has to the query set.
(C) Shows an example ROC curve from the cross validation described in the main text. 
Based on 3 randomly selected query nodes containing this GO term.
}
\label{fig:query_example}
\end{figure*}

@@

 \item \textbf{Yeast protein-protein interaction network (Yeast PPI)} \cite{yu2008high}
 This dataset is a collection of recorded binary interactions between proteins collected with high-throughput yeast-2-hybrid assays.
 The metadata used are known, experimentally validated protein complexes from \cite{pu2008up}.
 The network contains 6222 nodes in the largest connected component, with 22,3868 edges.
 There are 409 experimentally validated protein complexes, 236 of which contain 3 or more nodes.
 The protein complexes are typically very small in terms of number of proteins with  90\% of the complexes containing less than 10 proteins and only 2 complexes containing 50 or more proteins.

 \item \textbf{Arabidopsis protein-protein interaction network (Arabidopsis PPI)} \cite{ArabidopsisConsortium2011}
